### 2014-08-29 paper.tex
Added abstract and start of raw data section.

@@

>>>>

\begin{abstract}

  Herein we share a data set of typical gait data for 11 subjects walking at a
  three speeds on an instrumented treadmill while being longitudinally
  perturbed in the stance phase with psuedo-random fluctuations in the
  treadmill belt speed. We provide raw marker and ground reaction loads in
  addition to processed data that includes gait landmarks, 2D joint angles,
  angular rates, and joint torques. The protocol is described in detail along
  with the the additional meta data about each of the data files. This data can
  be useful for validating or genreating mathematical models that capable of
  simulating non-periodic and pertubed gaits.

\end{abstract}

@@

\section{Raw Data}

The raw data consists of a set of ASCII tab delimited text files output from
both the Mocap and Record modules in D-Flow in addition a YAML file that
contains all of the necessary meta data for the given trial. These three files
are stored in a hierarchy of directories with one trial per directory. The
directories are named in the following fashion \verb+T001/+ where \verb+T+
stands for ``trial'' and the following three digits are provide a unique trial
identification number.

\subsection{mocap-xxx.txt}

The output from the D-Flow mocap module is stored in a tab delimted file named
\verb+mocap-xxx.txt+ where \verb+xxx+ represents the trial id number. The file
contains several columns:

\begin{description}
  \item[TimeStamp] The system monotonically time when D-Flow recieves a frame
    from Cortex. These are approximately at 100 hz and given in seconds.
  \item[FrameNumber] Monotonically increasing integers that correspond to each
    frame received from Cortex.
  \item[Marker Coordinates] Any column that ends in \verb+.PosX+, \verb+.PosY+,
    or \verb+.PosZ+ are marker coordinates expressed in Cortex's Cartesian
    reference frame. These values are in meters.
  \item[Ground Reaction Loads] The left \verb+FP1+ and right \verb+FP2+ force
    plates output the forces and moments of the BLANK

Markers

We make use of the full body 47 marker set described in \cite{Ton's HBM paper}.
